Goes Here

### 2012-07-29 paper.tex
Intro

\section{Introduction}
\section{System Description}
\subsection{Input API}
Specification of an optimization problem using our API.
\subsection{Optimization Framework}
Describe four main components and some built-in libraries.
\section{Experiments}
\subsection{Previous Work}
Subsurface scattering. Mechanical properties
\subsection{Textured Model}
Input: a textured 3D model and
	measured Albedo of print material.

>>>>

\section{Introduction}
3D printing has the potential to dramatically reduce the required time and cost of
fabricating custom materials and objects. In particular, it allows the fabrication of materials with complex internal
structures that are difficult or impossible to manufacture with other technologies. Additive manufacturing could be
much more widely adopted and easier to use, given a high-fidelity translation from specifications of objects defined
in terms of their mechanical, optical, and appearance properties to output-device-specific computer
programs that produce the best possible approximation of these digital objects. However, this is still one of
the most important unsolved problems in digital direct manufacturing. Due to its combinatorial nature, this
problem becomes more and more challenging as the range of different printable materials increases. This paper
aims to provide an abstraction mechanism and a software framework for translating specifications to fabrication
instructions. It is possible to design a computationally efficient and general process for translating virtual objects
with desired mechanical, electrical, optical, and appearance properties into composite printable materials.
We will achieve this goal through a reduction-optimization-simulation approach.
\section{Previous Work}

\section{System Description}
The software framework (shown in Figure~\ref{fig:framework}) is composed of 
a set of software
modules that can be easily modified or exchanged. The first component
of this framework is an output-device-independent description API
that allows the user to specify any physical object in terms of its physical
properties such as geometry, mechanical behaviors, and appearance. 
The framework will also provide physically-based
simulation tools that accurately predict the behavior of our output device.
The goal of the optimization module is to search through
the space of possible device outputs and deliver one that best matches the
desired model. In order to evaluate the quality of the match between the
simulation output and the desired model we need to develop appropriate
comparison metrics. Finally, a central component of our framework is
a reduction model which makes the optimization problem tractable by
reducing the search space as much as possible.
The reduction model can specified by experts or deduced from a
set of examples. Next, we will describe each element of the framework in
more detail.
\begin{figure}
\caption{API overview}
\label{fig:framework}
\end{figure}
\subsection{Input API}
Our input API allows a designer to either
define material properties for sections of an object
or specify behavior of an object. 
The designer
can use functions to describe properties such as reflectance (e.g., BRDFs, BSSRDFs), 
stiffness, or other spatially varying properties. 
Although it is possible to define the object directly by only specifying material
properties, intuitive user
interfaces will aid in specifying the objects and their properties
in terms of intuitive metaphors.
For example, the elastic properties of an object can be specified by a set of
example displacements from the rest pose and the corresponding applied forces.
\subsection{Optimization Framework}
Describe four main components and some built-in libraries.
\section{Experiments}
\subsection{Previous Work}
Subsurface scattering. Mechanical properties
\subsection{Textured Model}
Input: a textured 3D model and
	measured Albedo of print material.
